An assessment of photometric redshift PDF performance in the context of LSST

### 2018-11-13 paper/tex/methods.tex
address EAZY algorithm problem

Here we outline the photo-$z$ PDF codes tested in this study. In total, eleven distinct codes are tested.  This sample is not comprehensive, codes were chosen based on the expertise available within the group; however, those chosen do cover a broad range of the current-generation codes.  Both template-based and machine learning approaches are included and each are described separately in Secs.~\ref{sec:templatecodes} and \ref{sec:trainingcodes} respectively. The list of codes are summarized in Table.~\ref{tab:list_of_codes}.  All code runners were asked to output redshift estimates on 200 linear-spaced bins between redshifts 0 and 2.

@@

\textsc{EAZY}\footnote{\url{https://github.com/gbrammer/eazy-photoz}} \citep[Easy and Accurate Photometric Redshifts from Yale,][]{Brammer:08} is a template-based photo-$z$ code that includes several features that improve on the basic $\chi^2$ fit used in many template codes. It can fit the observed photometry with SEDs created from a linear combination of a set of templates at each redshift, and the best-fit SED is found by simultaneously fitting one, two or all of the templates by minimizing $\chi^2$. The minimized $\chi^2(z)$ is then combined with an apparent magnitude prior to obtain the posterior redshift probability distribution, although some argue that this is not the mathematically correct way of calculating the posteriors. \textsc{EAZY} can also account for the uncertainties in the templates by adding an empirically derived template error in quadrature as a function of redshift to the flux errors.

>>>>

Here we outline the photo-$z$ PDF codes tested in this study. In total, eleven distinct codes are tested.  This sample is not comprehensive, codes were chosen based on the expertise available within the group; however, those chosen do cover a broad range of the current-generation methods used in the field.  Both template-based and machine learning approaches are included and each are described separately in Secs.~\ref{sec:templatecodes} and \ref{sec:trainingcodes} respectively. The list of codes are summarized in Table.~\ref{tab:list_of_codes}.  All code runners were asked to output redshift posterior estimates on 200 linear-spaced bins between redshifts 0 and 2.

@@

\textsc{EAZY}\footnote{\url{https://github.com/gbrammer/eazy-photoz}} \citep[Easy and Accurate Photometric Redshifts from Yale,][]{Brammer:08} is a template-based photo-$z$ code that includes several features that extend the basic $\chi^2$ fit used in many template codes.  The code can fit the observed photometry with SEDs created from a linear combination of a set of templates at each redshift, and the best-fit SED is found by simultaneously fitting one, two or all of the templates by minimizing $\chi^2$. The minimized $\chi^2(z)$ is then combined with an apparent magnitude prior to obtain the posterior redshift probability distribution.  On examination of the source code for EAZY, it appears that rather than marginalizing across all templates in the $\chi^2$ calculation, \textsc{EAZY} takes only the minimum value of $\chi^2$ at each redshift.  This improper marginalization does not lead to the correct posterior distribution, an implementation issue that will need to be addressed in the future.
%, although some argue that this is not the mathematically correct way of calculating the posteriors.
\textsc{EAZY} can also account for the uncertainties in the templates by adding an empirically derived template error in quadrature as a function of redshift to the flux errors.
